refnx - Neutron and X-ray reflectometry analysis in Python

### 2018-07-23 paper/manuscript.tex
PAPER: journal code
PAPER: middle initials

\documentclass[pdf,preprint]{iucr}
\RequirePackage{graphicx}
\journalcode{A}

@@

\begin{document}
\title{refnx - Neutron and X-ray reflectometry analysis in Python}
\cauthor[a]{Andrew}{Nelson}{andrew.nelson@ansto.gov.au}{}
\author[b]{Stuart~W.}{Prescott}

@@

\newcommand{\refnx}{\emph{refnx}}
\newcommand{\Objective}{\textbf{Objective}}
\newcommand{\GlobalObjective}{\textbf{GlobalObjective}}
\newcommand{\Parameter}{\textbf{Parameter}}
\newcommand{\Structure}{\textbf{Structure}}
\newcommand{\Slab}{\textbf{Slab}}
\newcommand{\Component}{\textbf{Component}}
\newcommand{\LipidLeaflet}{\textbf{LipidLeaflet}}
\newcommand{\Transform}{\textbf{Transform}}
\newcommand{\DataD}{\textbf{Data1D}}
\newcommand{\ReflectModel}{\textbf{ReflectModel}}
\newcommand{\Spline}{\textbf{Spline}}
\newcommand{\conda}{\emph{conda}}
\newcommand{\corner}{\emph{corner}}
\newcommand{\MixedReflectModel}{\textbf{MixedReflectModel}}
\newcommand{\pip}{\emph{pip}}
\newcommand{\emcee}{\emph{emcee}}
\newcommand{\ptemcee}{\emph{ptemcee}}
\newcommand{\NumPy}{\emph{NumPy}}
\newcommand{\SciPy}{\emph{SciPy}}
\newcommand{\Cython}{\emph{Cython}}
\newcommand{\Jupyter}{\emph{Jupyter}}
\newcommand{\ipywidgets}{\emph{ipywidgets}}

@@

The \Objective\ statistics are used directly by the \textbf{CurveFitter} class to perform least-square fitting or Bayesian MCMC of the system. \refnx\ uses the \SciPy\ package for least-squares analysis (DifferentialEvolution, Levenberg--Marquardt, LBFGSB - Limited Broyden--Fletcher--Goldfarb--Shanno with bounds) and the \emcee\ and \ptemcee\ packages \cite{emcee, ptemcee} for affine invariant MCMC ensemble sampling of the posterior distribution of the parameters. \ptemcee\ is a fork of \emcee\ that implements parallel tempering, for characterisation of multi-modal probability distributions; different modes can be traversed by chain populations at higher temperatures, while individual modes are efficiently explored by chains at lower temperatures.
The likelihoods used in MCMC and least-squares assume that the measurement errors are normally distributed, Equation~\ref{eqn:2}. However, other types of measurement errors (e.g. Poissonian) could be implemented by a subclass of \Objective\ overriding the log-likelihood method.
Parallelisation of the sampling is done automatically, and can use MPI on a cluster for greater parallelisation. Visualisation of the samples produced by MCMC sampling is done using the \corner\ package \cite{corner} for scatter plot matrices. On the conclusion of a fit/sampling run each \Parameter\ value is updated and given a standard error. For the sampling these represent the median and half the [15.87, 84.13] percentile range respectively; the latter approximating the standard deviation for a normally distributed statistic.

>>>>

\documentclass[pdf,preprint]{iucr}
\RequirePackage{graphicx}
\journalcode{J}

@@

\begin{document}
\title{refnx - Neutron and X-ray reflectometry analysis in Python}
\cauthor[a]{Andrew~R. J.}{Nelson}{andrew.nelson@ansto.gov.au}{}
\author[b]{Stuart~W.}{Prescott}

@@

\newcommand{\refnx}{\emph{refnx}}
\newcommand{\Objective}{\textbf{Objective}}
\newcommand{\CurveFitter}{\textbf{CurveFitter}}
\newcommand{\GlobalObjective}{\textbf{GlobalObjective}}
\newcommand{\Parameter}{\textbf{Parameter}}
\newcommand{\Structure}{\textbf{Structure}}
\newcommand{\Slab}{\textbf{Slab}}
\newcommand{\Component}{\textbf{Component}}
\newcommand{\LipidLeaflet}{\textbf{LipidLeaflet}}
\newcommand{\Transform}{\textbf{Transform}}
\newcommand{\DataD}{\textbf{Data1D}}
\newcommand{\ReflectModel}{\textbf{ReflectModel}}
\newcommand{\Spline}{\textbf{Spline}}
\newcommand{\conda}{\emph{conda}}
\newcommand{\corner}{\emph{corner}}
\newcommand{\MixedReflectModel}{\textbf{MixedReflectModel}}
\newcommand{\pip}{\emph{pip}}
\newcommand{\emcee}{\emph{emcee}}
\newcommand{\ptemcee}{\emph{ptemcee}}
\newcommand{\NumPy}{\emph{NumPy}}
\newcommand{\SciPy}{\emph{SciPy}}
\newcommand{\Cython}{\emph{Cython}}
\newcommand{\Jupyter}{\emph{Jupyter}}
\newcommand{\ipywidgets}{\emph{ipywidgets}}

@@

The \Objective\ statistics are used directly by the \CurveFitter\ class to perform least-square fitting or Bayesian MCMC of the system. \refnx\ uses the \SciPy\ package for least-squares analysis (DifferentialEvolution, Levenberg--Marquardt, LBFGSB - Limited Broyden--Fletcher--Goldfarb--Shanno with bounds) and the \emcee\ and \ptemcee\ packages \cite{emcee, ptemcee} for affine invariant MCMC ensemble sampling of the posterior distribution of the parameters. \ptemcee\ is a fork of \emcee\ that implements parallel tempering, for characterisation of multi-modal probability distributions; different modes can be traversed by chain populations at higher temperatures, while individual modes are efficiently explored by chains at lower temperatures.
The likelihoods used in MCMC and least-squares assume that the measurement errors are normally distributed, Equation~\ref{eqn:2}. However, other types of measurement errors (e.g. Poissonian) could be implemented by a subclass of \Objective\ overriding the log-likelihood method.
Parallelisation of the sampling is done automatically, and can use MPI on a cluster for greater parallelisation. Visualisation of the samples produced by MCMC sampling is done using the \corner\ package \cite{corner} for scatter plot matrices. On the conclusion of a fit/sampling run each \Parameter\ value is updated and given a standard error. For the sampling these represent the median and half the [15.87, 84.13] percentile range respectively; the latter approximating the standard deviation for a normally distributed statistic.
